Probabilistic Inference of Basic Stellar Parameters:\\ Application to Flickering Stars \altaffilmark{\titledag}

### 2015-06-08 version1.0/introduction.tex
test
v minor changes

@@

\citet{cranmer:2014} demonstrated that models of stellar surface granulation are 
indeed reproduce a flicker effect in close agreement with that observed by
\citet{bastien:2013}, providing a physically-plausible explanation. Since
surface gravity is highly correlated to mean stellar density (\rhostar) on
evolutionary tracks, \citet{kipping:2014} showed that flicker can be also
be used to infer \rhostar, which is more useful for exoplanet transit
analysis \citep{seager:2003}.

>>>>

TEST

@@

\citet{cranmer:2014} demonstrated that models of stellar surface granulation 
indeed reproduce a flicker effect in close agreement with that observed by
\citet{bastien:2013}, providing a physically-plausible explanation. Since
surface gravity is highly correlated to mean stellar density (\rhostar) on
evolutionary tracks, \citet{kipping:2014} showed that flicker can be also
be used to infer \rhostar, which is more useful for exoplanet transit
analysis \citep{seager:2003}.
